Biomass and species richness temporal trends drives the assembly and the disassembly of food-web in natural fish assemblages

### 2021-06-10 paper/appendix.Rmd
Spatial models

We kept all stations that had a significant trend (decrease or increase) for both
species richness and community biomass, with resulting 
`r length(st_mono_trends_rich_bm)` stations.

>>>>

We kept all stations that had a significant trend (decrease or increase) for both
species richness and community biomass, with resulting 
`r length(st_trends_rich_bm)` stations.

### 2021-06-10 paper/manuscript.Rmd
Spatial models

Biodiversity affects ecosystem properties such as total biomass, productivity
and stability [@tilman_biodiversity_2014; @loreau_biodiversity_2001]. However,
current biodiversity is at risk, numerous
studies reported dramatic declines of population and community biomass
[@ceballos_biological_2017; @hallmann_more_2017; @albano_native_2021], as well
as ongoing extinction [@barnosky_has_2011]. Consequences of such trends on various
aspects of community structure are not well-known whereas numerous ecological studies
have shown that the different aspects of community structure are tightly linked [REF].

The temporal trends of species richness and community biomass are likely to
affect community structure. The positive link between Biodiversity and ecosystem
functioning shown in experimental studies predict that loss and gain of species
richness should respectively result in loss and gain of community biomass
[@tilman_biodiversity_2014; @pennekamp_biodiversity_2018]. But this relation is
not always found in natural settings [@grace_integrative_2016;
@li_relationship_2018; @maureaud_biodiversityecosystem_2019]. Numerous
studies find relation between species richness and evenness, but their disagree
on the sign of the relationships [@soininen_relationship_2012; @ma_species_2005;
@maureaud_biodiversityecosystem_2019], highlighting the diversity of assembly
processes in ecological communities.

The distribution and the number of ecological interactions, i.e. the structure
of ecological networks, also covaries with species richness and community
biomass. In food-webs, connectance, which measures the degree of generalism in a
network, has been theoretically shown to theoretically positively scale with
community biomass [@thebault_food-web_2003]. Connectance has been also shown to
be negatively related to species richness in empirical food-webs
[@dunne_network_2006]. Trophic level has also been shown to be positively linked
to total biomass in theoretical models [@wang_biodiversity_2018]. All together,
these studies show that the different dimensions of network structure are
closely linked.

The space for time substitution allows to use the studies mentioned above to
predict how changes in species richness or community biomass will in turn affect
community and network structure. The hypothesis that space can
surrogate space is often implicitly made in ecological studies. This method
began to be widely used in the early 20th century to infer the temporal
succession of vegetation from space variations [@pickett_space-for-time_1989]. It
supposes a homology between variations in space and in time i.e. that spatial
sequences corresponds to temporal sequences. This method have raised criticisms
[@damgaard_critique_2019], with studies showing analogous patterns in space and time
[@blois_space_2013] or not [@johnson_testing_2008; @adler_contrasting_2007].
Spatial turnover of species composition, dispersal limitation, disturbance and
stochastic processes have been hypothesised to be responsible for the failure of
space for time substitution [@adler_contrasting_2007; @blois_space_2013].

In this line, how community biomass and species richness temporal trends are linked to
change in food-web structure is still an open question, as well as if space for
time substitution works to infer consequences of species richness and community
biomass on food-web structure. The increasing availability of ecological
temporal series makes possible to assess those questions.

>>>>

Biodiversity affects ecosystem properties such as total biomass, productivity
and stability [@tilman_biodiversity_2014; @loreau_biodiversity_2001]. However,
current biodiversity is at risk, numerous studies reported dramatic declines of
population and community biomass [@ceballos_biological_2017;
@hallmann_more_2017; @albano_native_2021], as well as decrease in species
richness 
[@barnosky_has_2011; @newbold_global_2015]. Consequences of such trends on
various aspects of community structure are not well-known whereas numerous
ecological studies have shown that the different aspects of community structure
are tightly linked [REF].

The temporal trends of species richness and community biomass are indeed
predicted to affect community structure. The positive link between Biodiversity
and ecosystem functioning shown in experimental studies predict that loss and
gain of species richness should respectively result in loss and gain of
community biomass [@tilman_biodiversity_2014; @pennekamp_biodiversity_2018]. But
this relation is not always found in natural settings [@grace_integrative_2016;
@li_relationship_2018; @maureaud_biodiversityecosystem_2019]. Numerous studies
find relation between species richness and evenness, but their disagree on the
sign of the relationships [@soininen_relationship_2012; @ma_species_2005;
@maureaud_biodiversityecosystem_2019], highlighting the diversity of assembly
processes in ecological communities.

The distribution and the number of ecological interactions, i.e. the structure
of ecological networks, also covaries with species richness and community
biomass. In food-webs, connectance, which measures the degree of generalism in a
network, has been theoretically shown to positively scale with
community biomass [@thebault_food-web_2003]. Connectance has been also shown to
be negatively related to species richness in empirical food-webs
[@dunne_network_2006]. Trophic level has also been shown to be positively linked
to total biomass in theoretical models [@wang_biodiversity_2018]. All together,
these studies show that the different dimensions of network structure are 
closely linked.

The links between the different component of community structure often come from
spatial gradient comparison. The space for time substitution allows to use the
studies mentioned above to predict how changes in species richness or community
biomass will in turn affect community and network structure. The hypothesis that
space can surrogate space is often implicitly made in ecological studies. This
method began to be widely used in the early 20th century to infer the temporal
succession of vegetation from space variations [@pickett_space-for-time_1989].
It supposes a homology between variations in space and in time i.e. that spatial
sequences corresponds to temporal sequences. This method have raised criticisms
[@damgaard_critique_2019], with studies showing analogous patterns in space and
time [@blois_space_2013] or not [@johnson_testing_2008;
@adler_contrasting_2007]. Spatial turnover of species composition, dispersal
limitation, disturbance and stochastic processes have been hypothesised to be
responsible for the failure of space for time substitution
[@adler_contrasting_2007; @blois_space_2013].

In this line, how community biomass and species richness temporal trends are
linked to temporal changes in food-web structure is still an open question, as
well as if space for time substitution works to infer consequences of species
richness and community biomass on food-web structure. The increasing
availability of ecological temporal series makes possible to assess those
questions.
